---
title: "Week 01 Assignment"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#### Exercises

1.  Explain coercion rules. Create an example that demonstrates the fixed order of the coercion rules.

```{r}
# If you call a function with an argument of a wrong type, R will coerce values to a different type so that the function will work.

c(1.5, "3") will bring the results c("1.5", "3")
```

2.  The following code will generate a warning. Explain why.

It is not displayed as proper numbers. It should read as.integer(c("1", "2", "3"))

```{r}
as.integer(c("one", "two", "three"))
```
```{r}
as.integer(c("1", "2", "3"))
```

3.  Create a vector of a sequence of integers starting at 2, ending at 100, and increasing by 2. Assign the vector to an object called `evens`. Coerce the vector to be of type `integer`. Confirm that the vector is of type `integer`.

```{r}
Evens = seq(from = 2, 
    to = 100, 
    by = 2) 


```

```{r}
Evens = as.integer(Evens)
```

```{r}
is.integer(Evens)
```


4.  Create a vector of random numbers with a length equal to your vector in exercise 3. Use a seed with a value of 730 before creating your vector. Assign the vector to an object called `randoms`. Confirm the type of the vector.

```{r}
set.seed(730)
randoms <- runif(n = 50, min = 0, max = 730) 

```
```{r}
is.numeric(randoms)
```


5.  Create a vector demonstrating which values in exercise 3 are greater than `0.75`. Assign the vector to an object called `logicals`. Confirm the type of the vector.

```{r}
logicals <- randoms > 0.75

``` 
```{r}
is.logical(logicals)
```

6.  Create a data frame including the three vectors created in exercises 3 through 5. Assign it to an object following best practices for naming.

```{r}
dataframe1 <- data.frame(randoms,Evens,logicals)

```

7.  Create a new object which is the sum of `evens` and `randoms` all divided by 3. Demonstrate how to calculate basic summary statistics for this new object (mean, median, minimum, maximum, standard deviation, variance).

```{r}

Sum <- c(Evens, randoms)/3


```

```{r}
mean(randoms)
median(randoms)
min(randoms)
max(randoms)
sd(randoms)
var(randoms)
```



8.  We discussed the idea that R is a "vectorized" language. Explain this concept. Why is it important?

Vectorized languages use vectors and arrays. It allows you to write code that is easy to read




9.  Run the `sessionInfo` function in a chunk.
```{r}
`sessionInfo`
```

